\bf Nonparametric Bootstrap KS Test with Stationary Time Series

### 2023-10-03 manuscript/manuscript.tex
New Simulations

@@

>>>>

The Kolgomorov-Smirnov (KS) test is a popular goodness-of-fit statistic that can
be used to assess how well a sample fits a given distribution.

@@

The rest of the paper is outlined as follows: in the first 
section, we assess whether the KS
test works under the null hypothesis, in the second section, we evaluate the 
test's 
power when the null hypothesis is false, and in the third section, we end with 
concluding remarks.

\section{Null Hypothesis}
\label{sec:null}

\section{Alternative Hypothesis}
\label{sec:alternative}
